Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-29 overview.tex
Adding missing references that I couldn't look up in the plane!

This PPM implementation does an excellent job of capturing strong
shocks in a few cells.  Multidimensional schemes are built up by
directional splitting and produce a method that is formally second
order-accurate in space and time and which explicitly conserves mass,
linear momentum, and energy.  \red{(REF?)}  A variety of Riemann
solvers have been implemented.

@@

\subsubsection{Godunov MUSCL (HD) with Dedner divergence cleaning (MHD)}
This solver was developed to attack problems in magnetic field
amplification during the formation of galaxies \citep{Wang:2009a} and
to understand the role of proto-stellar jets for the theory of star
formation \citep{Wang:2009b}. It combines the standard approach of
Godunov \citep{Godunov1959} for finite volume techniques with the
method of lines as described by \cite{leveque2002finite} and
\cite{toro-1997}. In addition, it implements the hyperbolic divergence
cleaning algorithm of \cite{2002JCoPh.175..645D}. It supports multiple
approximate Riemann solvers and non-ideal equations of
states. Consequently, these suite of solvers can be used for hydro and
magneto-hydrodynamic simulations. It is also this class of solvers as
well as a version of the PPM hydro solver which have been ported to
Nvidia's CUDA framework allowing \enzo\ to take advantage of modern
graphics hardware \citep{Wang:2010}.

>>>>

This PPM implementation does an excellent job of capturing strong
shocks in a few cells.  Multidimensional schemes are built up by
directional splitting and produce a method that is formally second
order-accurate in space and time and which explicitly conserves mass,
linear momentum, and energy \citep{Hawley84, Norman86}.  A variety of
Riemann solvers have been implemented.

@@

\subsubsection{Godunov MUSCL (HD) with Dedner divergence cleaning (MHD)}
This solver was developed to attack problems in magnetic field
amplification during the formation of galaxies \citep{Wang:2009a} and
to understand the role of proto-stellar jets for the theory of star
formation \citep{Wang:2009b}. It combines the standard approach of
Godunov \citep{Godunov1959} for finite volume techniques with the
method of lines as described by \cite{leveque2002finite} and
\cite{toro-1997}. In addition, it implements the hyperbolic divergence
cleaning algorithm of \cite{2002JCoPh.175..645D}. It supports multiple
approximate Riemann solvers and non-ideal equations of
states. Consequently, these suite of solvers can be used for hydro and
magneto-hydrodynamic simulations. It is also this class of solvers as
well as a version of the PPM hydro solver which have been ported to
nVidia's CUDA framework allowing \enzo\ to take advantage of modern
graphics hardware \citep{Wang:2010}.
